Community-Conditioned Language Models

### 2021-04-21 paper/paper.tex
actually the current scheme isn't so bad... just make the non-lower-case explicit

The vocabulary is drawn from the set of all words appearing with a frequency
greater than \num{5e-5} (1 in \num{2000}) in at least one community.
This results in a vocabulary size of \num{47403}, including a special
out-of-vocablary token.

%We use a vocabulary size of \num{40000} tokens, including a special
%out-of-vocabulary token.  The vocabulary consists of the most frequent
%tokens at the message level (across all communities), meaning that we
%only count each token once per message.  The main reason for this
%choice is to avoid over-counting otherwise rare tokens that were
%repeated many times in a single message.

>>>>

We use a vocabulary size of \num{40000} tokens, including a special
out-of-vocabulary token.  The vocabulary consists of the most frequent
tokens at the message level (across all communities), meaning that we
only count each token once per message.  The main reason for this
choice is to avoid over-counting otherwise rare tokens that were
repeated many times in a single message.
